---
title: "Eating Out"
author: "Robert solis"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---





## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
#require(haven)
require(foreign)
```
```{r, eval=TRUE,warning=FALSE}
#GSS <-(read_dta(file="GSS1998.dta))
GSS<- readstata13::read.dta13(file="GSS1998.dta")
GSS <-droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <-na.omit(mydata)

```




```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```
The white group eats out more then not, while the other groups eat out more then the black group and less then not.

```{r}
dd2 <- mydata %>% group_by(race,eatout) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=race,y=count,fill=eatout))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=race,y=prcnt*100,fill=eatout)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```
The one the left one is the count and the right is the percentage.

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
Here we have the numerical result. the percentage of whites eating out is on top percentile.While 70% of blacks ate out a total of 28 did not. The other group were the smallest, black group in the middle and white on top for eating out.



```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

There is a low P value of 000002287 Chi square statistics is 25.9769.
```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```
White people eat out almost 2.2 times more then black people. The p value of white people is greater then .005. The p value is lower for the black group. Fisher Xy is an analog to Tuku HD. The odd between black and white is somewhere at 0 between 1.49 and zero is in the middle range
.
#Conclusion
Today i learned how to tamper with and use Fisher Xy to get data and variables from other files like Strata GSS 1998 to see which race eats out more and eats in. It was a challenge and took two days but I am very joyful now thats its over. I've learned how to collect data from univeristys and caculate and display their results from the researchers.